---
title: "Homework 4"
author: "Tarun Manoharan"
date: "2024-02-16"
output: pdf_document
---

[https://github.com/TarunMano/SDS315_HW4](https://github.com/TarunMano/SDS315_HW4)

***

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.height=3, fig.width=4, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60))
```

```{r echo = FALSE, message = FALSE}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(mosaic)
```


## Problem 1

```{r echo = FALSE}
gasprices = read.csv("gasprices.csv")
```

### Theory 1

```{r echo = FALSE}
boot_comp = do(10000)*mean(Price~Competitors, data = mosaic::resample(gasprices))
conf_comp = confint(boot_comp, level = 0.95)
lowerM = round(conf_comp[1,2] - conf_comp[2,2],2)
higherM = round(conf_comp[1,3] - conf_comp[2,3],2)


ggplot(gasprices) + geom_boxplot(aes(x = Competitors, y = Price), fill = 'skyblue') + labs(title = "Price vs The Presence of a Competitor")
```

Gas stations charge more if they lack direct competition in sight, this theory is seemingly true, as according to the data. On average gas stations without a direct competitor have a price of somewhere between `r round(conf_comp[1,2],2)` and `r round(conf_comp[1,3],2)`, with 95% confidence. Gas stations with a direct competitor in sight however have a price of somewhere between `r round(conf_comp[2,2],2)` and `r round(conf_comp[2,3],2)`, with 95% confidence. As such the difference in price between having a direct competitor in sight and not is somewhere between `r lowerM` and `r higherM`. In conclusion the theory of if gas stations charge in the presence of a direct competitor is true by somewhere between 2 to 3 cents.

### Theory 2

```{r echo = FALSE, message = FALSE}
ggplot(gasprices,aes(x = Income, y = Price)) + geom_point() + geom_smooth(method = lm, color = "orange",fill = 'skyblue', se = TRUE) + labs(title = "Correlation between Income and Gas Price")

boot_rich = do(10000)*cor(Income~Price, data = mosaic::resample(gasprices))
conf_rich = confint(boot_rich, level = 0.95)


```


The richer the area, the higher the gas prices is somewhat false as according to the data. The correlation between income and price is somewhere between `r round(conf_rich[1,2],2)` and `r round(conf_rich[1,3],2)`, with 95% confidence, this means that there is not a somewhat weak correlation between Income and Price, and is further evidenced by the fact that there are low income areas with high price, and high income areas with lower prices. In conclusion, the theory that the richer the area, the higher the gas prices is false, due to there being a weak correlation between the two factors. 

### Theory 3

```{r echo = FALSE}

boot_light = do(10000)*mean(Price~Stoplight, data = mosaic::resample(gasprices))
conf_light = confint(boot_light, level = 0.95)

ggplot(gasprices) + geom_boxplot(aes(x = Stoplight, y = Price), fill = 'palegreen') + labs(title = "Price vs The Presence of a Stoplight")

```

The theory that gas stations at stoplights charge more is seemingly false, as according to the data. On average gas stations at a stoplight have a price of somewhere between `r round(conf_light[2,2],2)` and `r round(conf_light[2,3],2)`, with 95% confidence. While gas stations that are not in the presence of a stoplight on average have a price of somewhere between `r round(conf_light[1,2],2)` and `r round(conf_light[1,3],2)`, with 95% confidence. As such the difference between not having a stoplight and having one, is best estimated as `r round(conf_light[1,6] - conf_light[2,6],2)` cents. In conclusion the theory that gas stations at stoplights charge more is false, due to there being a surplus in price on average when there is no stoplight. 

### Theory 4

```{r echo = FALSE}

boot_highway = do(10000)*mean(Price~Highway, data = mosaic::resample(gasprices))
conf_highway = confint(boot_highway, level = 0.95)

ggplot(gasprices) + geom_boxplot(aes(x = Highway, y = Price), fill = 'pink') + labs(title = "Price vs The Presence of a Highway")

```

Gas stations with direct highway access charge more, this theory is seemingly true as according to the data. On average gas stations that are not in the presence of a highway have a price somewhere between `r round(conf_highway[1,2],2)` and `r round(conf_highway[1,3],2)`, and gas stations that are in the presence of a highway have a price somewhere between `r round(conf_highway[2,2],2)` and `r round(conf_highway[2,3],2)`, all with 95% confidence. As such the difference between the presence of a highway and not is best estimated as `r round(conf_highway[2,6] - conf_highway[1,6],2)`. In conclusion the theory that gas stations with direct highway access charge more is true, due to there being a surplus in the price on average when there is a highway. 

### Theory 5 

```{r echo = FALSE}
gasbrands = gasprices %>% mutate(Name = ifelse(Name != "Shell", yes= "Other Brands", no= "Shell"))

boot_brand = do(10000)*diffmean(Price~Name, data = mosaic::resample(gasbrands))
conf_brand = confint(boot_brand, level = 0.95)

ggplot(gasbrands) + geom_boxplot(aes(x = Name, y = Price), fill = '#f50c5a') + labs(title = "Price vs Shell and Competitors") 

```

Shell charges more than all other non-Shell brands, this theory is seemingly true according to the data. The difference in mean prices, can be said with 95% confidence is somewhere between `r round(conf_brand[1,2],2)` and `r round(conf_brand[1,3],2)`, with the best estimate being `r round(conf_brand[1,6],2)`. In conclusion the difference in means is less than 10 cents but still shows that on average Shell charges more than all other brands of gas stations. 

## Problem 2

```{r echo = FALSE}
sclass = read.csv("sclass.csv")
```

### Part A.

```{r echo = FALSE, message = FALSE}
sclass_AMG = sclass %>% filter(year == 2011 & trim == "63 AMG")
boot_amg = do(10000)*mean(~mileage, data = mosaic::resample(sclass_AMG))
conf_amg = confint(boot_amg, level = 0.95)
```
After using a bootsrapped 95% confidence interval on all the 2011 S-Class 63 AMG's that hit the used car market, the average mileage of these cars is somewhere between `r round(conf_amg[1,2])` and `r round(conf_amg[1,3])`, with 95% confidence. The best estimate of the mileage in these cars is `r round(conf_amg[1,6])`, also with 95% confidence 


### Part B. 

```{r echo = FALSE}
sclass_550 = sclass %>%  filter(year == 2014 & trim == "550")
sclass_550 = sclass_550 %>%  mutate(isBlack = ifelse(color == "Black", yes = TRUE, no = FALSE))

boot_550 = do(10000)*prop(~isBlack, data = mosaic::resample(sclass_550))
conf_550 = confint(boot_550, level = 0.95)
```

After using a bootstrapped 95% confidence interval on all the 2014 S-Class 550's, it can be said with 95% confidence that the proportion of these cars that were painted black is somewhere between `r round(conf_550[1,2],3) * 100`% and `r round(conf_550[1,3],3) * 100`%, with the best estimate being `r round(conf_550[1,6],3) * 100`%.

## Problem 3

```{r echo = FALSE}
nbc_pilotsurvey = read.csv("nbc_pilotsurvey.csv")
```

### Part A. 
```{r echo = FALSE}
nbc_ed_earl = nbc_pilotsurvey %>% filter(Show == "My Name is Earl"| Show == "Living with Ed")
boot_ed_earl = do(10000) * diffmean(Q1_Happy~Show, data = mosaic::resample(nbc_ed_earl))
conf_ed = confint(boot_ed_earl, level = 0.95)
```
1) Question: The question that is trying to be answered is that,  between the shows "My Name is Earl" and "Living with Ed", do one of the shows consistently produce a higher mean happiness response than the other?
2) Approach: The approach taken was to first filter the original "nbc_pilotsurvey" dataset to only include both of those shows. Then to take the new dataset and bootstrap it with 10000 resamples of the difference mean happiness rating for either show using the "do()" and "mosaic::resample()" functions. Finally, to construct the confidence interval, the function "confint()" was used on the bootstrapped data, using a 0.95 level.
3) Results: Between the shows, it can be said with 95% confidence, that "Living with Ed" on average has a higher happiness score than "My Name is Earl", with the difference being somewhere between `r round(conf_ed[1,2],2) * -1` and `r round(conf_ed[1,3],2) * -1`, with the best estimate being `r round(conf_ed[1,2],6) * -1`.
4) Conclusion: The results show that "Living with Ed" mostly had a higher mean happiness rating than "My Name is Earl", although the results showed minimal difference between the two scores it still is important to note that the difference was present, and should still be considered viable when considereing the happiness rating between the two shows. 

### Part B. 
```{r echo = FALSE}
nbc_big_LA = nbc_pilotsurvey %>% filter(Show == "The Biggest Loser" | Show == "The Apprentice: Los Angeles")
boot_bigLA = do(10000) * diffmean(Q1_Annoyed~Show, data = mosaic::resample(nbc_big_LA))
conf_la = confint(boot_bigLA, level = 0.95)

```

1) Question: The question that is trying to be answered is that, between the shows "The Biggest Loser" and "The Apprentice: Los Angeles", do one of the shows consistently produce a higher mean annoyed response than the other?
2) Approach: The approach taken was to first filter the original "nbc_pilotsurvey" dataset to only include both of those shows. Then to take the new dataset and bootstrap it with 10000 resamples of the difference mean annoyed rating for either show using the "do()" and "mosaic::resample()" functions. Finally, to construct the confidence interval, the function "confint()" was used on the bootstrapped data, using a 0.95 level.
3) Results: Between the two shows it can be said with 95% confidence that the show, "The Apprentice: Los Angeles", consistently produced a higher annoyed response than "The Biggest Loser", with the difference in average annoyed responses being somewhere between `round(conf_la[1,2],2) * -1` and `round(conf_la[1,3],2) * -1`, with the best estimate being `round(conf_la[1,6],2) * -1`.
4) Conclusion: The results show that the difference in annoyed response ratings between "The Apprentice: Los Angeles" and "The Biggest Loser" is statistically significant at the 5% level, because a 95% confidence interval for that difference fails to contain zero, thus showing that "The Apprentice: Los Angeles" is evidenced to consistently report a higher average annoyed response. 

### Part C. 
```{r echo = FALSE}
nbc_star = nbc_pilotsurvey %>%  filter(Show == "Dancing with the Stars")
nbc_star = nbc_star %>% mutate(above4 = ifelse(Q2_Confusing >= 4, yes = TRUE , no = FALSE))

boot_star = do(10000) * prop(~above4, data = mosaic::resample(nbc_star))
conf_star = confint(boot_star, level = 0.95)

```
1) Question: The question that is trying to be answered is that, what is the proportion of American TV watchers would give a response of 4 or greater to the question Q2_Confusing to the show 'Dancing with the Stars"?
2) Approach: The approach taken was to first filter the original "nbc_pilotsurvey" dataset to only contain the one TV show. Then to create a new variable using the "mutate()" function in the data set called "above4" to show whether or not the score given was above 4. Then to take the new dataset and bootstrap it with 10000 resamples of the proportion of above 4 ratings using the "do()" and "mosaic::resample()" functions. Finally, to construct the confidence interval, the function "confint()" was used on the bootstrapped data, using a 0.95 level.
3) Results: With 95% confidence, it can be said that the proportion of American TV watchers would rate above a 4 for the confused response is somewhere between `r round(conf_star[1,2],3)*100`% and `r round(conf_star[1,3],3)*100`%, with the best estimate being `r round(conf_star[1,6],3)*100`%.
4) Conclusion: The results show that the best guess of American TV Watchers of the show "Dancing with the Stars" that would respond 4 or above to the Q2_Confusing question is `r round(conf_star[1,6],3)*100`%, which is somewhat low, and that not many Americans who watch the show are overly confused by the show. 

## Problem 4.
```{r echo = FALSE}
ebay = read.csv("ebay.csv")
boot_ebay = do(10000) * diffmean(rev_ratio~adwords_pause, data = mosaic::resample(ebay))
conf_ebay = confint(boot_ebay, level = 0.95)
```

1) Question: The question trying to be answered is that whether or not using paid search advertising generated more revenue than not using paid search advertising.
2) Approach: the approach taken was to first bootstrap the dataset with 10000 resamples of the difference in means of the two test groups, using the "do()", and "mosaic::resample()" functions. Finally, to construct the confidence interval, the function "confint()" was used on the bootstrapped data, using a 0.95 level.
3) Results: With 95% confidence it can be said that the difference in mean revenue ratio between the treatment groups and the control groups is somewhere between `r round(conf_ebay[1,2],4)` and `r round(conf_ebay[1,3],4)`, with the best estimate being `r round(conf_ebay[1,6],4)`.
4) Conclusion: The results show that although there is a difference there is not a systematically lower difference between the two, showing that the use of paid search advertising is not really driving revenue, and that is most likely a waste of money.
